\section{Beheadings}
\label{beheadings}

\begin{intro}
  Herein these four cases involving disqualification come up for recitation.
\end{intro}

\setsubsecheadstyle{\subsubsectionFmt}
\pdfbookmark[3]{Disqualification 1}{disq1}
\subsection*{\hyperref[par1]{Disqualification 1: The training precept on the act of sexual intercourse}}
\label{disq1}
If any bhikkhu [who] has entered upon the training and livelihood for bhikkhus, not having rejected the training, not having disclosed [his] incapability, should engage in the act of sexual intercourse, even with just a female animal, he is disqualified, not in communion.

\pdfbookmark[3]{Disqualification 2}{disq2}
\subsection*{\hyperref[par2]{Disqualification 2: The training precept on the taking of what has not been given}}
\label{disq2}
If any bhikkhu should take [what has] not been given from a village or wilderness-area, which is reckoned as theft, [and] the taking of what has not been given [is] of the kind [that] on account of [it] kings, having caught the robber, would physically punish or imprison or banish [him, saying]: ``You are a robber! You are a fool! You are insane! You are a thief!,'' a bhikkhu taking [what has] not been given of such a kind, is also disqualified, not in communion.

\pdfbookmark[3]{Disqualification 3}{disq3}
\subsection*{\hyperref[par3]{Disqualification 3: The training precept on (killing) a human being}}
\label{disq3}
If any bhikkhu should deliberately deprive a human being of life, or should seek an assassin for him, or should praise the attractiveness of death, or should incite [him] to death [saying]: ``Dear man, what [use] is this bad, wretched life for you? Death is better than life for you!'' should he, [having] such thought-and mind, [having such-] thought-and-intention, praise in manifold ways the beauty of death or incite [him] to death, he also is disqualified, not in communion.

\pdfbookmark[3]{Disqualification 4}{disq4}
\subsection*{\hyperref[par4]{Disqualification 4: The training precept on superhuman states}}
\label{disq4}
If any bhikkhu, [though] not directly knowing [it], should claim a superhuman state pertaining to himself, [a state of] knowing and seeing [that is] suitable for the noble [ones], [saying]: ``Thus I know! Thus I see!,'' [and] then, on another occasion, [whether] being interrogated or not being interrogated, having committed [the offence], desiring purification, should say so: ``[Although] not knowing [it,] I spoke thus [saying]: 'I know,' not seeing [it, I spoke, saying:] 'I see.' I bluffed vainly [and] falsely,'' except [when said] in overestimation, he also is disqualified, not in communion.

\medskip

\begin{center}
Venerables, the four cases involving disqualification have been recited, a bhikkhu who has committed any one of them, does not obtain the communion with bhikkhus. As [he was] before, so [he is] after [committing it]: he is one who is disqualified, not in communion.

\smallskip

Concerning that I ask the Venerables: [Are you] pure in this?\\
A second time again I ask: [Are you] pure in this?\\
A third time again I ask: [Are you] pure in this?

\smallskip

The venerables are pure in this, therefore there is silence, so do I bear this [in mind].
\end{center}

\begin{outro}
  The recitation of the [cases involving] disqualification is finished
\end{outro}

\clearpage
