\section{Trainings}
\label{trainings}

\begin{intro}
  Venerables, these cases related to the training come up for recitation.
\end{intro}

\setsubsecheadstyle{\subsectionFmt}
\subsection{The Section on Being Even All Around}
\vspace{0.2cm}

\pdfbookmark[3]{Training 1 \& 2}{training1-2}
\subsubsection*{\hyperref[sekh1-2]{Training 1 \& 2: The training precept on being even all around}}
\label{training1-2}
``I shall wear [the under-robe] even all around,'' thus the training is to be done.\\
``I shall wrap [the outer-robes] even all around,'' thus the training is to be done.

\pdfbookmark[3]{Training 3 \& 4}{training3-4}
\subsubsection*{\hyperref[sekh3-4]{Training 3 \& 4: The training precept on being well covered}}
\label{training3-4}
``I shall go well covered inside an inhabited area,'' thus the training is to be done.\\
``I shall sit well covered inside an inhabited area,'' thus the training is to be done.

\pdfbookmark[3]{Training 5 \& 6}{training5-6}
\subsubsection*{\hyperref[sekh5-6]{Training 5 \& 6: The training precept on being well restrained}}
\label{training5-6}
``I shall go well-restrained inside an inhabited area,'' thus the training is to be done.\\
``I shall sit well-restrained inside an inhabited area,'' thus the training is to be done.

\pdfbookmark[3]{Training 7 \& 8}{training7-8}
\subsubsection*{\hyperref[sekh7-8]{Training 7 \& 8: The training precept on the eyes cast down}}
\label{training7-8}
``I shall go with the eyes cast down inside an inhabited area,'' thus the training is to be done.\\
``I shall sit with the eyes cast down inside an inhabited area,'' thus the training is to be done.

\pdfbookmark[3]{Training 9 \& 10}{training9-10}
\subsubsection*{\hyperref[sekh9-10]{Training 9 \& 10: The training precept on (robes) lifted up}}
\label{training9-10}
``I shall not go with [robes] lifted up inside an inhabited area,'' thus the training is to be done.\\
``I shall not sit with [robes] lifted up inside an inhabited area,'' thus the training is to be done.

\begin{center}
  The section [starting with the rule] on being even all round is first
\end{center}

\setsubsecheadstyle{\subsectionFmt}
\subsection{The Section on Loud Laughter}
\vspace{0.2cm}

\pdfbookmark[3]{Training 11 \& 12}{training11-12}
\subsubsection*{\hyperref[sekh11-12]{Training 11 \& 12: The training precept on loud laughter}}
\label{training11-12}
``I shall not go with loud laughter inside an inhabited area,'' thus the training is to be done.\\
``I shall not sit with loud laughter inside an inhabited area,'' thus the training is to be done.

\pdfbookmark[3]{Training 13 \& 14}{training13-14}
\subsubsection*{\hyperref[sekh13-14]{Training 13 \& 14: The training precept on loud sounds}}
\label{training13-14}
``I shall go quiet[ly] inside an inhabited area,'' thus the training is to be done.\\
``I shall sit quiet[ly] inside an inhabited area,'' thus the training is to be done.

\pdfbookmark[3]{Training 15 \& 16}{training15-16}
\subsubsection*{\hyperref[sekh15-16]{Training 15 \& 16: The training precept on swaying the body}}
\label{training15-16}
``I shall not go swaying the body inside an inhabited area,'' thus the training is to be done.\\
``I shall not sit swaying the body inside an inhabited area,'' thus the training is to be done.

\pdfbookmark[3]{Training 17 \& 18}{training17-18}
\subsubsection*{\hyperref[sekh17-18]{Training 17 \& 18: The training precept on swaying the arms}}
\label{training17-18}
``I shall not go swaying the arms inside an inhabited area,'' thus the training is to be done.\\
``I shall not sit swaying the arms inside an inhabited area,'' thus the training is to be done.

\pdfbookmark[3]{Training 19 \& 20}{training19-20}
\subsubsection*{\hyperref[sekh19-20]{Training 19 \& 20: The training precept on swaying the head}}
\label{training19-20}
``I shall not go swaying the head inside an inhabited area,'' thus the training is to be done.\\
``I shall not sit swaying the head inside an inhabited area,'' thus the training is to be done.

\begin{center}
  The section [starting with the rule] on loud laughter is second
\end{center}

\setsubsecheadstyle{\subsectionFmt}
\subsection{The Section on Making Into a Prop}
\vspace{0.2cm}

\pdfbookmark[3]{Training 21 \& 22}{training21-22}
\subsubsection*{\hyperref[sekh21-22]{Training 21 \& 22: The training precept on making into a prop}}
\label{training21-22}
``I shall not go having made [the arms] a prop inside an inhabited area,'' thus the training is to be done.\\
``I shall not sit having made [the arms] a prop inside an inhabited area,'' thus the training is to be done.

\pdfbookmark[3]{Training 23 \& 24}{training23-24}
\subsubsection*{\hyperref[sekh23-24]{Training 23 \& 24: The training precept on being (with the head) covered}}
\label{training23-24}
``I shall not go with [the head] covered inside an inhabited area,'' thus the training is to be done.\\
``I shall not sit with [the head] covered inside an inhabited area,'' thus the training is to be done.

\pdfbookmark[3]{Training 25}{training25}
\subsubsection*{\hyperref[sekh25]{Training 25: The training precept on crouching}}
\label{training25}
``I shall not go in a crouching [posture] inside an inhabited area,'' thus the training is to be done.

\pdfbookmark[3]{Training 26}{training26}
\subsubsection*{\hyperref[sekh26]{Training 26: The training precept on (knees being) clasped around}}
\label{training26}
``I shall not sit with the [knees] clasped-around inside an inhabited area,'' thus the training is to be done.

\pdfbookmark[3]{Training 27}{training27}
\subsubsection*{\hyperref[sekh27]{Training 27: The training precept on accepting in a respectul manner}}
\label{training27}
``I shall accept alms-food appreciatively,'' thus the training is to be done.

\pdfbookmark[3]{Training 28}{training28}
\subsubsection*{\hyperref[sekh28]{Training 28: The training precept on paying attention to the bowl (while) accepting}}
\label{training28}
``I shall accept alms-food paying attention to the bowl,'' thus the training is to be done.

\pdfbookmark[3]{Training 29}{training29}
\subsubsection*{T\hyperref[sekh29]{raining 29: The training precept on accepting curry in the proper proportion}}
\label{training29}
``I shall accept alms-food which has curry in the proper proportion,'' thus the training is to be done.

\pdfbookmark[3]{Training 30}{training30}
\subsubsection*{\hyperref[sekh30]{Training 30: The training precept on (alms-food) level with the rim}}
\label{training30}
``I shall accept alms-food which is level with the rim,'' thus the training is to be done.

\begin{center}
  The section [starting with the rule] on making into a prop is third
\end{center}

\setsubsecheadstyle{\subsectionFmt}
\subsection{The Section on Eating in a Respectful Manner}
\vspace{0.2cm}

\pdfbookmark[3]{Training 31}{training31}
\subsubsection*{\hyperref[sekh31]{Training 31: The training precept on eating in a respectful manner}}
\label{training31}
``I shall eat alms-food appreciatively,'' thus the training is to be done.

\pdfbookmark[3]{Training 32}{training32}
\subsubsection*{\hyperref[sekh32]{Training 32: The training precept on paying attention (while) eating}}
\label{training32}
``I shall eat alms-food paying attention to the bowl,'' thus the training is to be done.

\pdfbookmark[3]{Training 33}{training33}
\subsubsection*{\hyperref[sekh33]{Training 33: The training precept on (eating) systematically}}
\label{training33}
``I shall eat alms-food systematically,'' thus the training is to be done.

\pdfbookmark[3]{Training 34}{training34}
\subsubsection*{\hyperref[sekh34]{Training 34: The training precept on the proper proportion}}
\label{training34}
``I shall eat alms-food which has curry in the proper proportion,'' thus the training is to be done.

\pdfbookmark[3]{Training 35}{training35}
\subsubsection*{\hyperref[sekh35]{Training 35: The training precept on (alms-food) not made into a heap}}
\label{training35}
I shall not eat alms-food, having pressed [it] down into a shall heap,'' thus the training is to be done.

\pdfbookmark[3]{Training 36}{training36}
\subsubsection*{\hyperref[sekh36]{Training 36: The training precept on covering with rice}}
\label{training36}
``I shall not cover curry or condiment with rice out of liking for more,'' thus the training is to be done.

\pdfbookmark[3]{Training 37}{training37}
\subsubsection*{\hyperref[sekh37]{Training 37: The training precept on suggesting rice or curry}}
\label{training37}
``I shall not eat curry or rice, [when] not ill, having requested [it] for his own benefit, thus the training is to be done.

\pdfbookmark[3]{Training 38}{training38}
\subsubsection*{\hyperref[sekh38]{Training 38: The training precept on finding fault}}
\label{training38}
``I shall not look at another's bowl finding fault,'' thus the training is to be done.

\pdfbookmark[3]{Training 39}{training39}
\subsubsection*{\hyperref[sekh39]{Training 39: The training precept on morsels}}
\label{training39}
``I shall not make an over-large morsel [of food],'' thus the training is to be done.

\pdfbookmark[3]{Training 40}{training40}
\subsubsection*{\hyperref[sekh40]{Training 40: The training precept on pieces (of food)}}
\label{training40}
``I shall eat a round piece [of food],'' thus the training is to be done.

\begin{center}
  The section [starting with the rule] on respectful manner is fourth
\end{center}

\setsubsecheadstyle{\subsectionFmt}
\subsection{The Section on Morsels of Food}
\vspace{0.2cm}

\pdfbookmark[3]{Training 41}{training41}
\subsubsection*{\hyperref[sekh41]{Training 41: The training precept on what has not been brought to (the mouth)}}
\label{training41}
``I shall not open the mouth when the morsel [of food] has not been brought to [it],'' thus the training is to be done.

\pdfbookmark[3]{Training 42}{training42}
\subsubsection*{\hyperref[sekh42]{Training 42: The training precept on eating}}
\label{training42}
I shall not put the whole hand onto the mouth while eating,'' thus the training is to be done.

\pdfbookmark[3]{Training 43}{training43}
\subsubsection*{\hyperref[sekh43]{Training 43: The training precept on having a morsel (of food)}}
\label{training43}
``I shall not speak with a mouth which has a morsel [of food in it],'' thus the training is to be done.

\pdfbookmark[3]{Training 44}{training44}
\subsubsection*{\hyperref[sekh44]{Training 44: The training precept on the tossing up of bits (of food)}}
\label{training44}
``I shall not eat tossing up bits [of food],'' thus the training is to be done.

\pdfbookmark[3]{Training 45}{training45}
\subsubsection*{\hyperref[sekh45]{Training 45: The training precept on biting off a morsel}}
\label{training45}
``I shall not eat biting off a morsel [of food],'' thus the training is to be done.

\pdfbookmark[3]{Training 46}{training46}
\subsubsection*{\hyperref[sekh46]{Training 46: The training precept on puffing up the cheeks}}
\label{training46}
``I shall not eat puffing up [the cheeks],'' thus the training is to be done.

\pdfbookmark[3]{Training 47}{training47}
\subsubsection*{\hyperref[sekh47]{Training 47: The training precept on shaking off the hand}}
\label{training47}
``I shall not eat shaking [food] off the hand,'' thus the training is to be done.

\pdfbookmark[3]{Training 48}{training48}
\subsubsection*{\hyperref[sekh48]{Training 48: The training precept on scattering rice grains}}
\label{training48}
I shall not eat scattering rice-grains,'' thus the training is to be done.

\pdfbookmark[3]{Training 49}{training49}
\subsubsection*{\hyperref[sekh49]{Training 49: The training precept on sticking out the tongue]}}
\label{training49}
``I shall not eat sticking out the tongue,'' thus the training is to be done.

\pdfbookmark[3]{Training 50}{training50}
\subsubsection*{\hyperref[sekh50]{Training 50: [The training precept on making chomping (sounds)}}
\label{training50}
``I shall not eat making chomping [sounds],'' thus the training is to be done.

\begin{center}
  The section [starting with the rule] on morsels of food is fifth
\end{center}

\setsubsecheadstyle{\subsectionFmt}
\subsection{The Section on Slurping}
\vspace{0.2cm}

\pdfbookmark[3]{Training 51}{training51}
\subsubsection*{\hyperref[sekh51]{Training 51: The training precept on making slurping (sounds)}}
\label{training51}
``I shall not eat making slurping [sounds],'' thus the training is to be done.

\pdfbookmark[3]{Training 52}{training52}
\subsubsection*{\hyperref[sekh52]{Training 52: The training precept on licking the hand}}
\label{training52}
I shall not eat licking the hand,'' thus the training is to be done.

\pdfbookmark[3]{Training 53}{training53}
\subsubsection*{\hyperref[sekh53]{Training 53: The training precept on licking the bowl}}
\label{training53}
``I shall not eat licking the bowl,'' thus the training is to be done.

\pdfbookmark[3]{Training 54}{training54}
\subsubsection*{\hyperref[sekh54]{Training 54: The training precept on licking the lips}}
\label{training54}
``I shall not eat licking the lip[s],'' thus the training is to be done.

\pdfbookmark[3]{Training 55}{training55}
\subsubsection*{\hyperref[sekh55]{Training 55: The training precept on (a hand soiled) with food}}
\label{training55}
``I shall not accept a drinking-water cup with a hand which is [soiled] with food,'' thus the training is to be done.

\pdfbookmark[3]{Training 56}{training56}
\subsubsection*{\hyperref[sekh56]{Training 56: The training precept on (bowl-washing water) with rice grains}}
\label{training56}
``I shall not throw away bowl-washing water which has rice-grains [in it] in an inhabited area,'' thus the training is to be done.

\pdfbookmark[3]{Training 57}{training57}
\subsubsection*{\hyperref[sekh57]{Training 57: The training precept on the sunshade in (his) hand}}
\label{training57}
``I shall not teach Dhamma to one who has a sunshade in [his] hand, [and] who is not ill,'' thus the training is to be done.

\pdfbookmark[3]{Training 58}{training58}
\subsubsection*{\hyperref[sekh58]{Training 58: The training precept on the stick in (his) hand}}
\label{training58}
``I shall not teach Dhamma to one who has a stick in [his] hand, [and] who is not ill,'' thus the training is to be done.

\pdfbookmark[3]{Training 59}{training59}
\subsubsection*{\hyperref[sekh59]{Training 59: The training precept on the knife in (his) hand}}
\label{training59}
``I shall not teach Dhamma to one who has a knife in [his] hand [and] who is not ill,'' thus the training is to be done.

\pdfbookmark[3]{Training 60}{training60}
\subsubsection*{\hyperref[sekh60]{Training 60: The training precept on the weapon in (his) hand}}
\label{training60}
``I shall not teach Dhamma to one who has a weapon in [his] hand, [and] who is not ill,'' thus the training is to be done.

\begin{center}
  The section [starting with the rule] on slurping is sixth
\end{center}

\setsubsecheadstyle{\subsectionFmt}
\subsection{The Section on Shoes}
\vspace{0.2cm}

\pdfbookmark[3]{Training 61}{training61}
\subsubsection*{\hyperref[sekh61]{Training 61: The training precept on shoes}}
\label{training61}
``I shall not teach Dhamma to one who is wearing shoes, [and] who is not ill,'' thus the training is to be done.

\pdfbookmark[3]{Training 62}{training62}
\subsubsection*{\hyperref[sekh62]{Training 62: The training precept on sandals}}
\label{training62}
``I shall not teach Dhamma to one who is wearing sandals, [and] who is not ill,'' thus the training is to be done.

\pdfbookmark[3]{Training 63}{training63}
\subsubsection*{\hyperref[sekh63]{Training 63: The training precept on vehicles}}
\label{training63}
``I shall not teach Dhamma to one who is in a vehicle, [and] who is not ill,'' thus the training is to be done.

\pdfbookmark[3]{Training 64}{training64}
\subsubsection*{\hyperref[sekh64]{Training 64: The training precept on couches}}
\label{training64}
``I shall not teach Dhamma to one who is on a couch, [and] who is not ill,'' thus the training is to be done.

\pdfbookmark[3]{Training 65}{training65}
\subsubsection*{\hyperref[sekh65]{Training 65: The training precept on (knees being) clasped around}}
\label{training65}
``I shall not teach Dhamma to one sitting with [the knees] clasped-around, [and] who is not ill,'' thus the training is to be done.

\pdfbookmark[3]{Training 66}{training66}
\subsubsection*{\hyperref[sekh66]{Training 66: The training precept on being wrapped}}
\label{training66}
``I shall not teach Dhamma to one whose head is wrapped [with a turban], [and] who is not ill,'' thus the training is to be done.

\pdfbookmark[3]{Training 67}{training67}
\subsubsection*{\hyperref[sekh67]{Training 67: The training precept on being covered}}
\label{training67}
``I shall not teach Dhamma to one whose head is covered, [and] who is not ill,'' thus the training is to be done.

\pdfbookmark[3]{Training 68}{training68}
\subsubsection*{\hyperref[sekh68]{Training 68: The training precept on (sitting) on the ground}}
\label{training68}
``Having sat down on the ground, I shall not teach Dhamma, to one who is sitting on a seat, [and] who is not ill,'' thus the training is to be done.

\pdfbookmark[3]{Training 69}{training69}
\subsubsection*{\hyperref[sekh69]{Training 69: The training precept on a low seat}}
\label{training69}
``Having sat down on a low seat, I shall not teach Dhamma to one who is sitting on a high seat [and] who is not ill,'' thus the training is to be done.

\pdfbookmark[3]{Training 70}{training70}
\subsubsection*{\hyperref[sekh70]{Training 70: The training precept on standing}}
\label{training70}
``I shall not teach Dhamma [while] standing, to one who is sitting, [and] who is not ill,'' thus the training is to be done.

\pdfbookmark[3]{Training 71}{training71}
\subsubsection*{\hyperref[sekh71]{Training 71: The training precept on going behind}}
\label{training71}
``I shall not teach Dhamma [while] walking behind, to one who is going in front, [and] who is not ill,'' thus the training is to be done.

\pdfbookmark[3]{Training 72}{training72}
\subsubsection*{\hyperref[sekh72]{Training 72: The training precept on going off the path}}
\label{training72}
``I shall not teach Dhamma [while] walking off the path to one walking on the path, [and] who is not ill,'' thus the training is to be done.

\pdfbookmark[3]{Training 73}{training73}
\subsubsection*{\hyperref[sekh73]{Training 73: The training precept on excreting while standing}}
\label{training73}
``I shall not excrete or urinate [while] standing [and while] not ill,'' thus the training is to be done.

\pdfbookmark[3]{Training 74}{training74}
\subsubsection*{\hyperref[sekh74]{Training 74: The training precept on excreting on crops}}
\label{training74}
``I shall not excrete or urinate or spit on crops, [while] not ill,'' thus the training is to be done.

\pdfbookmark[3]{Training 75}{training75}
\subsubsection*{\hyperref[sekh75]{Training 75: The training precept on excreting in water}}
\label{training75}
``I shall not excrete or urinate or spit in water, [while] not ill,'' thus the training is to be done.

\begin{center}
  The section [starting with the rule] on shoes is seventh
\end{center}

\medskip

\begin{center}
Venerables, the cases related to the training have been recited.

\smallskip

Concerning that I ask the Venerables: [Are you] pure in this?\\
A second time again I ask: [Are you] pure in this?\\
A third time again I ask: [Are you] pure in this?

\smallskip

The Venerables are pure in this, therefore there is silence, thus I keep this [in mind].
\end{center}

\begin{outro}
  The cases related to the training have finished
\end{outro}

\clearpage
